Implementation of an Open-Source modular mangetic field camera hardware for usage in Low-Field MRI Systems

### 2023-10-13 documentation/paper/main.tex
.

@@

\subsection{Calibration Run}

cli einstellungen
+ ergebnis

@@

>>>>

\subsection{Calibration strategy \label{ref_calib}}

@@

For this purpose, the framework was extended by a CLI-based batch processing, which allows measurements of all sensors with the appropriate calibration measurements (offset, temperature) to be processed automatically.
The parameterisation is done by means of a customised configuration file in which the folders for raw and calibration measurements are specified.
The assignment is then done by a regex rule.

@@

\begin{figure}[htbp]
\centerline{\includegraphics[width=8cm]{magnets_with_holder.jpg}}
\caption{12x12x12mm N45 neodymium test magnets }
\label{mag_with_holder_fig}
\end{figure}

The test setup used consists of an 8x8 sensor array, which consists of 8 sensor slices with 8 TLV493d sensors each.
The test objects to be characterised were 12x12x12mm N45 neodymium magnets \ref{mag_with_holder_fig}.
These were mounted in a 3D-printed backlash-free holder with a distance of 10mm to the top of the sensor board \ref{mag_pcb_side_cut_fig}.

\begin{figure}[htbp]
\centerline{\includegraphics[width=8cm]{magnet_pcb_drawing.png}}
\caption{Sectional side cut: circle marks the center point of manget with sensor pcb on the bottom}
\label{mag_pcb_side_cut_fig}
\end{figure}
